---
title: "Missing Data Analysis"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r, setup, include=FALSE}
## set global chunk options
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

This script performs missing data analysis on the training data.

## Load Libraries

Load libraries to perform missing data analyses.

```{r}
### here for project directory navigation
library(here)

### tidyverse for data manipulation and plotting
library(tidyverse)

### naniar for missing data analysis
library(naniar)

### missForest for imputing missing values
library(missForest)

### doParallel for parallel computing
library(doParallel)

### doRNG for random seeds
library(doRNG)
```

## Load Data

Load data to analyze.

```{r}
### load data
## training set
train <- read_csv(here("data", "raw", "training_data.csv"))

### load data
## development set
development <- read_csv(here("data", "raw", "development_data.csv"))

### load data
## testing set
testing <- read_csv(here("data", "raw", "participant_test.csv"))
```

## Clean Data

Convert variables to appropriate types.

```{r}
### update training set
## save as object
train_work <- train %>%
  ## select variables
  select(Overall_Rating:PScale13_Q5) %>%
  ## update variables
  mutate(
    # ordinal factors
    across(
      # columns
      .cols = c(PScale01_Q1:PScale13_Q5),
      # function
      .fns = factor,
      # ordered
      ordered = TRUE
    ),
    # nominal factors
    across(
      # columns
      .cols = c(
        # situational judgment, biodata
        matches("SJ_(Most|Least)|Biodata"),
        # outcomes
        High_Performer, Protected_Group, Retained
      ),
      # function
      .fns = as_factor
    ),
    # integer values
    across(
      # columns
      .cols = c(
        # scenario scores
        matches("Scenario.*\\d$")
      ),
      # function
      .fns = as.integer
    )
  )

## preview
glimpse(train_work)

### update training set
## save as object
development_work <- development %>%
  ## select variables
  select(SJ_Most_1:PScale13_Q5) %>%
  ## update variables
  mutate(
    # ordinal factors
    across(
      # columns
      .cols = c(PScale01_Q1:PScale13_Q5),
      # function
      .fns = factor,
      # ordered
      ordered = TRUE
    ),
    # nominal factors
    across(
      # columns
      .cols = c(
        # situational judgment, biodata
        matches("SJ_(Most|Least)|Biodata")
      ),
      # function
      .fns = as_factor
    ),
    # integer values
    across(
      # columns
      .cols = c(
        # scenario scores
        matches("Scenario.*\\d$")
      ),
      # function
      .fns = as.integer
    )
  )

## preview
glimpse(development_work)

### update training set
## save as object
testing_work <- testing %>%
  ## select variables
  select(SJ_Most_1:PScale13_Q5) %>%
  ## update variables
  mutate(
    # ordinal factors
    across(
      # columns
      .cols = c(PScale01_Q1:PScale13_Q5),
      # function
      .fns = factor,
      # ordered
      ordered = TRUE
    ),
    # nominal factors
    across(
      # columns
      .cols = c(
        # situational judgment, biodata
        matches("SJ_(Most|Least)|Biodata")
      ),
      # function
      .fns = as_factor
    ),
    # integer values
    across(
      # columns
      .cols = c(
        # scenario scores
        matches("Scenario.*\\d$")
      ),
      # function
      .fns = as.integer
    )
  )

## preview
glimpse(testing_work)
```

## Missing Data Analysis

Examine patterns of missing data for the training data sets.

```{r}
### missing data by cases
## percentage of missing values by case
miss_case_summary(train_work)

## percentage of missing cases by number of missing values
miss_case_table(train_work)

### missing data by variables
## percentage of missing responses by variable
miss_var_summary(train_work) 

## percentage of missing responses by number of missing variables
miss_var_table(train_work)

### missing data by cases
## percentage of missing values by case
miss_case_summary(development_work)

## percentage of missing cases by number of missing values
miss_case_table(development_work)

### missing data by variables
## percentage of missing responses by variable
miss_var_summary(development_work) 

## percentage of missing responses by number of missing variables
miss_var_table(development_work)
```

## Imputation

Impute missing data.

### Random Forests

Use random forests to impute missing data.
Works best on feature items.

```{r}
### alter class of training data
## change class
class(train_work) <- class(train_work)[3]

### alter class of training data
## change class
class(development_work) <- class(development_work)[3]

### alter class of training data
## change class
class(testing_work) <- class(testing_work)[3]

### set-up parallel computing
## register
registerDoParallel(cores = 8)

## seed
registerDoRNG(seed = 101)

### impute missing values
## save as object
sjt_biodata_imp_res <- missForest(
  # data
  testing_work %>%
    # select variables
    select(matches("SJ_(Most|Least)|Biodata")),
  # parallel
  parallelize = "forests",
  # provide iteration information
  verbose = TRUE,
  # number of trees
  ntree = 800,
  # maximum iterations
  maxiter = 4
)

## register sequential
registerDoSEQ()

## check imputation error
sjt_biodata_imp_error <- tibble(
  # extract variable name
  var = names(train_work)[
    # find indexes for variables
    matches(
      # variable sets
      "SJ_(Most|Least)|Biodata", 
      # variable names      
      vars = names(train_work)
    )
  ],
  # error type
  error_type = names(sjt_biodata_imp_res$OOBerror),
  # error values
  error_value = sjt_biodata_imp_res$OOBerror
) %>%
  ## update variables
  mutate(
    # make RMSE
    error_value = if_else(
      # condition
      error_type == "MSE", 
      # true
      sqrt(error_value), 
      # false
      error_value
    ),
    # alter label
    error_type = if_else(
      # condition
      error_type == "MSE",
      # true
      "RMSE",
      # false
      error_type
    )
  )

## imputed values
sjt_biodata_imp <- sjt_biodata_imp_res$ximp

### set-up parallel computing
## register
registerDoParallel(cores = 8)

## seed
registerDoRNG(seed = 101)

### impute missing values
## save as object
scenario_imp_res <- missForest(
  # data
  testing_work %>%
    # select variables
    select(matches("Scenario.*\\d$")),
  # parallel
  parallelize = "forests",
  # provide iteration information
  verbose = TRUE,
  # number of trees
  ntree = 800,
  # maximum iterations
  maxiter = 4
)

## register sequential
registerDoSEQ()

## check imputation error
scenario_imp_error <- tibble(
  # extract variable name
  var = names(train_work)[
    # find indexes for variables
    matches(
      # variable sets
      "Scenario.*\\d$", 
      # variable names      
      vars = names(train_work)
    )
  ],
  # error type
  error_type = names(scenario_imp_res$OOBerror),
  # error values
  error_value = scenario_imp_res$OOBerror
) %>%
  ## update variables
  mutate(
    # make RMSE
    error_value = if_else(
      # condition
      error_type == "MSE", 
      # true
      sqrt(error_value), 
      # false
      error_value
    ),
    # alter label
    error_type = if_else(
      # condition
      error_type == "MSE",
      # true
      "RMSE",
      # false
      error_type
    )
  )

## imputed values
scenario_imp <- scenario_imp_res$ximp

### set-up parallel computing
## register
registerDoParallel(cores = 8)

## seed
registerDoRNG(seed = 101)

### impute missing values
## save as object
personality_imp_res <- missForest(
  # data
  testing_work %>%
    # select variables
    select(matches("PScale")),
  # parallel
  parallelize = "forests",
  # provide iteration information
  verbose = TRUE,
  # number of trees
  ntree = 800,
  # maximum iterations
  maxiter = 4
)

## register sequential
registerDoSEQ()

## check imputation error
personality_imp_error <- tibble(
  # extract variable name
  var = names(train_work)[
    # find indexes for variables
    matches(
      # variable sets
      "PScale", 
      # variable names      
      vars = names(train_work)
    )
  ],
  # error type
  error_type = names(personality_imp_res$OOBerror),
  # error values
  error_value = personality_imp_res$OOBerror
) %>%
  ## update variables
  mutate(
    # make RMSE
    error_value = if_else(
      # condition
      error_type == "MSE", 
      # true
      sqrt(error_value), 
      # false
      error_value
    ),
    # alter label
    error_type = if_else(
      # condition
      error_type == "MSE",
      # true
      "RMSE",
      # false
      error_type
    )
  )

## imputed values
personality_imp <- personality_imp_res$ximp

### set-up parallel computing
## register
registerDoParallel(cores = 8)

## seed
registerDoRNG(seed = 101)

### impute missing values
## save as object
time_imp_res <- missForest(
  # data
  testing_work %>%
    # select variables
    select(matches("Time")) %>%
    # update variables
    mutate(
      # replace 0 with NA
      across(
        # all columns
        .cols = everything(),
        # function
        .fns = ~ na_if(., 0)
      ),
      # apply function to columns
      across(
        # columns
        .cols = everything(),
        # function
        .fns = log
      )
    ),
  # parallel
  parallelize = "forests",
  # provide iteration information
  verbose = TRUE,
  # number of trees
  ntree = 800,
  # maximum iterations
  maxiter = 4
)

## register sequential
registerDoSEQ()

## check imputation error
time_imp_error <- tibble(
  # extract variable name
  var = names(train_work)[
    # find indexes for variables
    matches(
      # variable sets
      "Time", 
      # variable names      
      vars = names(train_work)
    )
  ],
  # error type
  error_type = names(time_imp_res$OOBerror),
  # error values
  error_value = time_imp_res$OOBerror
) %>%
  ## update variables
  mutate(
    # make RMSE
    error_value = if_else(
      # condition
      error_type == "MSE", 
      # true
      sqrt(error_value), 
      # false
      error_value
    ),
    # alter label
    error_type = if_else(
      # condition
      error_type == "MSE",
      # true
      "RMSE",
      # false
      error_type
    )
  )

## imputed values
time_imp <- time_imp_res$ximp

### set-up parallel computing
## register
registerDoParallel(cores = 4)

## seed
registerDoRNG(seed = 101)

### impute missing values
## save as object
dev_imp_res <- missForest(
  # data
  development_work %>%
    # select variables
    select(SJ_Most_1:PScale13_Q5),
  # parallel
  #parallelize = "forests",
  # OOB error
  variablewise = TRUE,
  # provide iteration information
  verbose = TRUE,
  # number of variables to try
  mtry = 10,
  # number of trees
  ntree = 1000,
  # maximum iterations
  maxiter = 5
)

## register sequential
registerDoSEQ()

## check imputation error
train_imp_error <- tibble(
  # extract variable name
  var = names(train_work)[
    # find indexes for variables
    matches(
      # variable sets
      "SJ|Scenario|Biodata|PScale", 
      # variable names      
      vars = names(train_work)
    )
  ],
  # error type
  error_type = names(train_imp_res$OOBerror),
  # error values
  error_value = train_imp_res$OOBerror
) %>%
  ## update variables
  mutate(
    # make RMSE
    error_value = if_else(
      # condition
      error_type == "MSE", 
      # true
      sqrt(error_value), 
      # false
      error_value
    ),
    # alter label
    error_type = if_else(
      # condition
      error_type == "MSE",
      # true
      "RMSE",
      # false
      error_type
    )
  )

## imputed values
train_imp <- dev_imp_res$ximp

### set-up parallel computing
## register
registerDoParallel(cores = 4)

## seed
registerDoRNG(seed = 101)

### impute missing values
## save as object
outcome_imp_res <- missForest(
  # data
  train_work %>%
    # select variables
    select(Overall_Rating:High_Performer),
  # parallel
  parallelize = "forests",
  # OOB error
  variablewise = TRUE,
  # provide iteration information
  verbose = TRUE,
  # number of variables to try
  mtry = 2,
  # number of trees
  ntree = 5,
  # maximum iterations
  maxiter = 5,
  # minimum size of terminal nodes
  nodesize = list(1, 5),
  # stratification
  strata = list(
    # numeric variables
    NULL, NULL, NULL, NULL, NULL,
    # categorical variables
    c(0.604, 0.396)
  ),
  # class weights
  classwt = list(
    # numeric variables
    NULL, NULL, NULL, NULL, NULL,
    # categorical variables
    c(19.99, 50)
  ),
  # cutoff
  cutoff = list(
    # numeric variables
    1, 1, 1, 1, 1,
    # categorical variables
    c(0.9999999999, 0.0000000001)
  )
)

## register sequential
registerDoSEQ()

## check imputation error
outcome_imp_error <- tibble(
  # extract variable name
  var = names(train_work)[
    # find first index
    matches(
      # variable
      "Overall_Rating", 
      # variable names      
      vars = names(train_work)
    ):
      # find second index
      matches(
        # variable
        "High_Performer", 
        # variable names
        vars = names(train_work)
      )
  ],
  # error type
  error_type = names(outcome_imp_res$OOBerror),
  # error values
  error_value = outcome_imp_res$OOBerror
) %>%
  ## update variables
  mutate(
    # make RMSE
    error_value = if_else(
      # condition
      error_type == "MSE", 
      # true
      sqrt(error_value), 
      # false
      error_value
    ),
    # alter label
    error_type = if_else(
      # condition
      error_type == "MSE",
      # true
      "RMSE",
      # false
      error_type
    )
  )

## imputed values
outcome_imp <- outcome_imp_res$ximp
```

## Save Objects

Save created objects.

```{r}
### save imputed data
## call function
write_csv(
  # imputed data
  sjt_biodata_imp,
  # path
  file = here("data", "imputed", "sjt_biodata_mf_test.csv")
)

### save errors of imputed data
## call function
write_csv(
  # imputed data
  sjt_biodata_imp_error,
  # path
  file = here("data", "imputed", "sjt_biodata_mf_errors.csv")
)

### save imputed data
## call function
write_csv(
  # imputed data
  scenario_imp,
  # path
  file = here("data", "imputed", "scenario_mf_test.csv")
)

### save errors of imputed data
## call function
write_csv(
  # imputed data
  scenario_imp_error,
  # path
  file = here("data", "imputed", "scenario_mf_errors.csv")
)

### save imputed data
## call function
write_csv(
  # imputed data
  personality_imp,
  # path
  file = here("data", "imputed", "personality_mf_test.csv")
)

### save errors of imputed data
## call function
write_csv(
  # imputed data
  personality_imp_error,
  # path
  file = here("data", "imputed", "personality_mf_errors.csv")
)

### save imputed data
## call function
write_csv(
  # imputed data
  time_imp,
  # path
  file = here("data", "imputed", "time_mf_test.csv")
)

### save errors of imputed data
## call function
write_csv(
  # imputed data
  time_imp_error,
  # path
  file = here("data", "imputed", "time_sing_mf_errors.csv")
)

### save imputed data
## call function
write_csv(
  # imputed data
  train_imp,
  # path
  file = here("data", "imputed", "train_sing_mf_all_items.csv")
)

### save errors of imputed data
## call function
write_csv(
  # imputed data
  train_imp_error,
  # path
  file = here("data", "imputed", "train_mf_all_items_errors.csv")
)

### save imputed data
## call function
write_csv(
  # imputed data
  outcome_imp,
  # path
  file = here("data", "imputed", "outcome_mf.csv")
)

### save errors of imputed data
## call function
write_csv(
  # imputed data
  outcome_imp_error,
  # path
  file = here("data", "imputed", "outcome_mf_errors.csv")
)
```
